Light inextensible strings under tension in the Schwarzschild geometry

### 2019-05-21 string_jpam.tex
fixes #5
fixes #7
fixes #8
fixes #11

\begin{equation}\label{radial_string_length}
  \int_{r=r_1}^{r_2}\frac{dr}{\sqrt{1-1/r}}=
  \left.
  \sqrt{r(r-1)} +\frac{1}{2}\log\left(
  \frac{r+\sqrt{r-1}}{r-\sqrt{r-1}}\right)
  \right|_{r_1}^{r_2}
  \end{equation}

@@

\begin{equation}
  \ell  =\frac{1}{2} + \log(2) + w + \frac{1}{8}w^{-1} + O(w^{-2}),
\end{equation}

\noindent suggesting that there is ``extra radial space'', of length
over $1.19$ Schwarzschild radii, sensible at large distances from the
event horizon.  This might suggest that radial strings have longer
proper length than expected.

@@

There does not appear to be a simple analytical solution but
nevertheless we may make several observations.
Equation~\ref{rdashdash} is a second-order nonlinear ordinary
differential equation and thus has two constants of integration.
There are two qualitatively different types of solutions: those with a
tangential point ($r'=0,r>1$), and those without.  Consider first
solutions with such a point: there exists a pair~$\left(r,\phi\right),
r>1$ at which~$r'(\phi)=0$.  By Rolle's theorem, this point must be
unique, as~$r''(\phi)>0$, and be the closest approach of the string to
the event horizon.

>>>>

\begin{equation}\label{radial_string_length}
  \int_{r=r_1}^{r_2}\frac{dr}{\sqrt{1-1/r}}=
  \left.
  \sqrt{r(r-1)} +\frac{1}{2}\log\left(
  \frac{\sqrt{r}+\sqrt{r-1}}{\sqrt{r}-\sqrt{r-1}}\right)
  \right|_{r_1}^{r_2}
  \end{equation}

@@

\begin{equation}
  \ell = w +  \frac{1}{2}\log w + \frac{1}{2} + \log(2)  +  \frac{1}{8}w^{-1} + O(w^{-2}),
\end{equation}

\noindent suggesting that there is ``extra radial space'', of length
over $1.19$ Schwarzschild radii, sensible at large distances from the
event horizon.  Radial strings have proper length longer than the
Schwarzschild radial coordinate difference $w$.

@@

There does not appear to be a simple analytical solution but
nevertheless we may make several observations.
Equation~\ref{rdashdash} is a second-order nonlinear ordinary
differential equation and thus has two constants of integration.
There are two qualitatively different types of solutions: those with a
tangential point ($r'=0,r>1$), and those without.  Consider first
solutions with such a point: there exists a pair~$\left(r,\phi\right),
r>1$ at which~$r'(\phi)=0$.  This point must be unique,
as~$r''(\phi)>0$, and be the closest approach of the string to the
event horizon.
